Parallel for Oregon Zip and WRF_Grid Intersection Proportion

### 2017-03-29 r_scripts/parallel_presentation.Rmd
revise

clusterExport(cl, "or_zip_map", envir = .GlobalEnv)
clusterExport(cl, "or_zip_name", envir = .GlobalEnv)
clusterExport(cl, "smoke_grid", envir = .GlobalEnv)
clusterExport(cl, "wrf_grid_name", envir = .GlobalEnv)
clusterExport(cl, "zip_polygon", envir = .GlobalEnv)
clusterExport(cl, "wrf_polygon", envir = .GlobalEnv)

>>>>

clusterExport(cl, "or_zip_map", envir = .GlobalEnv)
clusterExport(cl, "or_zip_name", envir = .GlobalEnv)
clusterExport(cl, "smoke_grid", envir = .GlobalEnv)
clusterExport(cl, "wrf_grid_name", envir = .GlobalEnv)
clusterExport(cl, "zip_wrf_proportion", envir = .GlobalEnv)
